Hunting experience and prey predictability jointly shape individual foraging specialisation in a predator-prey videogame

### 2022-05-18 manuscript/Chapter3-manuscript.Rmd
update manuscript. delete workspace

\newpage
# Abstract {.unnumbered}
Key points in this study:

- How experience shapes individual specialisation
  - H1: experience increases the range of behaviors and plasticity by reducing costs to swithing
  - H2: optimizing/refinement process - specialize with time - increase success)

- Prey predictability shapes individual foraging specialization
  - H1: prey predictability is positively correlated to behavioral predictability

- Specialist hunters will fare better on short timescales, when prey predictability is higher
- Generalist hunters will fare better on longer timescales, as they follow prey fluctuations
- Both types of hunters will thus achieve similar hunting success over the sampling period

@@

Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [sources].
*Ideas* : 
- * usually measured at the population level*
- * we now have metrics that enable the quantification of individual specialization*

@@

Hunting experience has been proposed as a potential major driver of the relationship between foraging specialisation and resource use [sources]. Learning how to hunt is crucial for young predators to reach adulthood and survive. (check Urszan et al)

@@

(learning optimises return rates or foraging success)
(apprentissage, search images, prior information)
(par contre, décomposer l'âge de l'expérience est difficile, et particulièrement chez des espèces sur le terrain puisque ça peut impliquer des techniques invasives)
(parler des études qui ont montré que certains spécialistes étaient meilleurs, mais que c'était confondu par l'âge)

>>>>

\newpage
# Abstract {.unnumbered}

@@

Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [@limaPuttingPredatorsBack2002, @schreiberCommunityEffectsPhenotypic2011, @pettorelliChapterTwoIndividual2015]. Studies report for many predator species that populations are often comprised of an assemblage of individuals specialising in different foraging strategies or resources [].

*Ideas* : 
- * usually measured at the population level*
- *effets de l'âge, blablabla*
- * we now have metrics that enable the quantification of individual specialization*

@@

Hunting experience has been proposed as a potential major driver of the relationship between foraging specialisation and resource use [sources]. Learning how to hunt is crucial for young predators to reach adulthood and survive. (check Urszan et al)
(learning optimises return rates or foraging success)
(apprentissage, search images, prior information)
(par contre, décomposer l'âge de l'expérience est difficile, et particulièrement chez des espèces sur le terrain puisque ça peut impliquer des techniques invasives)
(parler des études qui ont montré que certains spécialistes étaient meilleurs, mais que c'était confondu par l'âge)

@@
